---
title: "VizUM Miami Parks Data: A Visual Essay"
author: "Carter Allen"
date: "1/30/2018"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE, warning=FALSE)
```

## Intro

Data comes from [Miami-Dade County](https://opendata.miamidade.gov/Infrastructure/Parks-Facities/wjhr-nx6u) open data page. 

Load data and format the `Location 1` column to be split into `lat` and `lon`.
```{r}
library(tidyverse)
parks <- read_csv("parks.csv") %>%
  mutate(loc = (str_replace_all(`Location 1`,"\\(|\\)| ","")))
```

Separate `loc` into `lat` and `lon` using the comma as the delimiter and make sure they are in numeric form. 
```{r}
library(magrittr)
parks %<>%
  separate(loc,c("lat","lon"),",") %>%
  mutate(lat = as.numeric(lat),
         lon = as.numeric(lon))
```

Plot the park locations on a map of the Miami area. 
```{r}
library(leaflet)
leaflet(data = parks) %>%
  addTiles() %>%
  addMarkers(~lon,~lat)
```

It looks like there is one location that was incorrectly specified (it is in Africa!). The point was entered as (0,0). We can ignore this point by filtering to make sure both `lat` and `lon` are not 0.

```{r}
parks %<>%
  filter(lat != 0 & lon != 0)
```

The map has a label that gives the name of the park the mouse it hovering over. 
```{r}
library(htmltools)
leaflet(data = parks) %>%
  addTiles() %>%
  addCircleMarkers(~lon,~lat,
                   label = ~htmlEscape(name),
                   radius = 6,
                   stroke = FALSE,
                   fillOpacity = 0.5)
```

Would like to give points a size that is based on their acreage given in the `TOTACRE` column. Define a function that can categorize acreages. 

```{r}
categorize_size <- function(a)
{
  if(0 <= a & a <= 1.1)
  {
    return("Small Park")
  }
  else if(1.1 < a & a <= 5)
  {
    return("Medium Park")
  }
  else if(5 < a & a <= 12.8825)
  {
    return("Large Park")
  }
  else
  {
    return("Very Large Park")
  }
}
```

```{r}
categorize_sizes <- function(a_vec)
{
  b_vec = as.character(a_vec)
  l = length(a_vec)
  for(i in 1:l)
  {
    b_vec[i] = categorize_size(a_vec[i])
  }
  return(b_vec)
}
```

```{r}
parks %<>%
  mutate(park_size = categorize_sizes(parks$TOTACRE))
```

Mapping parks with 4 distinct size categories.

```{r}
leaflet(data = parks) %>%
  addTiles() %>%
  addCircleMarkers(~lon,~lat,
                   label = ~htmlEscape(paste(name,": A",TYPE,CLASS)),
                   radius = ~ifelse(park_size == "Small Park",3,
                                   ifelse(park_size == "Medium Park",6,
                                          ifelse(park_size == "Large Park",9,12))),
                   stroke = FALSE,
                   fillOpacity = 0.35)
```

```{r}
pal <- colorFactor(c("red","green"),c("No","Yes"))
```

```{r}
leaflet(data = parks) %>%
  addTiles() %>%
  addCircleMarkers(~lon,~lat,
                   label = ~htmlEscape(paste(name,": A",TYPE,CLASS)),
                   radius = ~ifelse(park_size == "Small Park",3,
                                   ifelse(park_size == "Medium Park",6,
                                          ifelse(park_size == "Large Park",9,12))),
                   stroke = FALSE,
                   fillOpacity = 0.35,
                   color = ~pal(BEACH))
```

